The Genetic Algorithm of GMSE

### 2020-05-23 notebook/ms/SI1.Rmd
Fix reference
Author name change, more to follow

---
title: 'The Genetic Algorithm of GMSE'
subtitle: 'GMSE: an R package for generalised management strategy evaluation (Supporting Information 1)'
author: A. Bradley Duthie&#xb9;&#xb3;, Jeremy J. Cusack&#xb9;, Isabel L. Jones&#xb9;,
  Jeroen Minderman&#xb9;, Erlend B. Nilsen&#xb2;, Roc&#0237;o A. Pozo&#xb9;, 
  O. Sarobidy Rakotonarivo&#xb9;, Bram Van Moorter&#xb2;, and Nils Bunnefeld&#xb9;
date: "[1] Biological and Environmental Sciences, University of Stirling, Stirling, UK
[2] Norwegian Institute for Nature Research, Trondheim, Norway [3] alexander.duthie@stir.ac.uk"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes:
linestretch: 1
bibliography: gmse.bib
biblio-style: apalike
link-citations: true
linkcolor: blue
---

@@

Here we explain how the fitnesses of candidate manager and user strategies in a `POPULATION` array (see above) are calculated. We emphasise that the fitness functions used in GMSE v0.4.0.7 are intended to be heuristic tools for identifying reasonable manager and user behaviours. In practice, our fitness functions identify behaviours that are well-aligned with manager and user interests for harvesting or crop yield, but they are not intended to identify *optimal* decisions. This practical, metaheuristic approach is consistent with the objectives of management strategy evaluation [@Bunnefeld2011], and is well-suited for the use of genetic algorithms [@Hamblin2013]. @Luke2013 describes the metaheuristic approach more generally (original emphasis retained):

>>>>

---
title: 'The Genetic Algorithm of GMSE'
subtitle: 'GMSE: an R package for generalised management strategy evaluation (Supporting Information 1)'
author: |
        | A. Bradley Duthie&#xb9;&#xb3;, Jeremy J. Cusack&#xb9;, Isabel L. Jones&#xb9;, Jeroen Minderman&#xb9;, 
        | Erlend B. Nilsen&#xb2;, Roc&#0237;o A. Pozo&#xb9;, O. Sarobidy Rakotonarivo&#xb9;, 
        | Bram Van Moorter&#xb2;, and Nils Bunnefeld&#xb9;'
[2] Norwegian Institute for Nature Research, Trondheim, Norway [3] alexander.duthie@stir.ac.uk"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes:
- \usepackage{lineno}
- \linenumbers
linestretch: 1
bibliography: gmse.bib
biblio-style: apalike
link-citations: true
linkcolor: blue
---

@@

Here we explain how the fitnesses of candidate manager and user strategies in a `POPULATION` array (see above) are calculated. We emphasise that the fitness functions used in GMSE v0.4.0.7 are intended to be heuristic tools for identifying reasonable manager and user behaviours. In practice, our fitness functions identify behaviours that are well-aligned with manager and user interests for harvesting or crop yield, but they are not intended to identify *optimal* decisions. This practical, metaheuristic approach is consistent with the objectives of management strategy evaluation [@Bunnefeld2011], and is well-suited for the use of genetic algorithms [@Hamblin2013]. @Luke2009 describes the metaheuristic approach more generally (original emphasis retained):
